\textbf{Selective DNA and Protein Isolation from Marine Macrophyte Surfaces}

### 2021-03-25 submission/manuscript.tex
Format text.
Review done.

\hypertarget{summary}{%
\subsection{Summary}\label{summary}}

@@

Leaves of \emph{C. nodosa} were sampled in a \emph{C. nodosa} meadow in
the Bay of Saline, northern Adriatic Sea (\ang{45;7;5} N, \ang{13;37;20}
E) and in a \emph{C. nodosa} meadow invaded by \emph{C. cylindracea} in
the Bay of Funtana, northern Adriatic Sea (\ang{45;10;39} N,
\ang{13;35;42} E). Thalli of \emph{C. cylindracea} were sampled in the
same \emph{C. nodosa} invaded meadow in the Bay of Funtana and at a
locality of only \emph{C. cylindracea} located in the proximity of the
invaded meadow. Leaves and thalli for 16S rRNA analysis, metagenomics
and metaproteomics were collected in two contrasting seasons, on 4
December 2017 (16S rRNA analysis and metaproteomics), 14 December 2017
(metagenomics) and 18 June 2018 (16S rRNA analysis, metagenomics and
metaproteomics). During spring 2018, the \emph{C. nodosa} meadow in the
Bay of Saline decayed to an extent that no leaves could be retrieved
(Najdek et al., 2020). In addition, as not enough DNA for both
metagenomic and 16S RNA analysis were obtained during the sampling on 4
December 2017, an additional sampling on 14 December 2017 was carried
out in the Bay of Funtana. Leaves and thalli were collected by diving
and transported to the laboratory in containers placed on ice and filled
with seawater from this site. Upon arrival to the laboratory, \emph{C.
nodosa} leaves were cut into sections of 1 -- 2 \si{\cm}, while \emph{C.
cylindracea} thalli were cut into 5 -- 8 \si{\cm} long sections. Leaves
and thalli were washed three times with sterile artificial seawater
(ASW) to remove loosely attached microbial cells.

@@

An aliquot of isolated DNA was treated with RNase A (final concentration
200 \si{\ug\per\ml}) for 2 \si{\hour} at 37 \si{\degreeCelsius}. The DNA
concentration was determined using the Quant-iT PicoGreen dsDNA Assay
Kit (Invitrogen, USA) according to the manufacturer's instructions and
diluted to 1 \si{\ng\per\ul}. The V4 region of the 16S rRNA gene was
amplified using a two-step PCR procedure. In the first PCR the 515F
(\(5'\)-GTGYCAGCMGCCGCGGTAA-\(3'\)) and 806R
(\(5'\)-GGACTACNVGGGTWTCTAAT-\(3'\)) primers from the Earth Microbiome
Project
(\url{http://press.igsb.anl.gov/earthmicrobiome/protocols-and-standards/16s/})
were used to amplify the target region (Caporaso et al., 2012; Apprill
et al., 2015; Parada et al., 2016). These primers contained on their
\(5'\) end a tagged sequence. Each sample was amplified in four parallel
25 \si{\ul} reactions of which each contained 1 × Q5 Reaction Buffer,
0.2 \si{\milli\Molar} of dNTPmix, 0.7 \si{\mg\per\ml} BSA (Bovine Serum
Albumin), 0.2 \si{\micro\Molar} of forward and reverse primers, 0.5 U of
Q5 High-Fidelity DNA Polymerase (New England Biolabs, USA) and 5
\si{\ng} of DNA template. Cycling conditions were: initial denaturation
at 94 \si{\degreeCelsius} for 3 \si{\minute}, 20 cycles of denaturation
at 94 \si{\degreeCelsius} for 45 \si{\s}, annealing at 50
\si{\degreeCelsius} for 60 \si{\s} and elongation at 72
\si{\degreeCelsius} for 90 \si{\s}, finalized by an elongation step at
72 \si{\degreeCelsius} for 10 \si{\minute}. The four parallel reactions
volumes were pooled and PCR products were purified using the GeneJET PCR
Purification Kit (Thermo Fisher Scientific, USA) according to the
manufacturer's instructions and following the protocol that included
isopropanol addition for better small DNA fragment yield. The column was
eluted in 30 \si{\ul} of deionized water. Purified PCR products were
sent for Illumina MiSeq sequencing (2 × 250 bp) at IMGM Laboratories,
Martinsried, Germany. Before sequencing at IMGM, the second PCR
amplification of the two-step PCR procedure was performed using primers
targeting the tagged region incorporated in the first PCR. In addition,
these primers contained adapter and sample-specific index sequences. The
second PCR was carried out for 8 cycles. Beside samples, a positive and
negative control were sequenced. A negative control was comprised of
four parallel PCR reactions without DNA template, while for a positive
control a mock community composed of evenly mixed DNA material
originating from 20 bacterial strains (ATCC MSA-1002, ATCC, USA) was
used. Partial 16S rRNA sequences obtained in this study have been
deposited in the European Nucleotide Archive (ENA) at EMBL-EBI under
accession numbers SAMEA6786270, SAMEA6648792 -- SAMEA6648794,
SAMEA6648809 -- SAMEA6648811 and SAMEA6648824.

@@

Isolated proteins were whole trypsin digested using the FASP
(filter-aided sample preparation) Protein Digestion Kit (Expedeon, UK)
according to the manufacturer's instructions with small modifications
(Wiśniewski et al., 2009). Prior to loading the solution onto the
column, protein pellets were solubilized in a urea sample buffer
included in the kit amended with DTT (final concentration 100
\si{\milli\Molar}) for 45 \si{\minute} at room temperature and
centrifuged at 20,000 × g for 2 -- 5 \si{\minute} at room temperature to
remove larger particles. The first washing step after protein solution
loading was repeated twice. In addition, the centrifugation steps were
prolonged if the column was clogged. Trypsin digestion was performed on
column filters at 37 \si{\degreeCelsius} overnight for 18 \si{\hour}.
The final filtrate containing peptides was acidified with 1
\si{\percent} (final concentration) trifluoroacetic acid (TFA), freezed
at \num{-80} \si{\degreeCelsius}, lyophilized and sent to VIME -- Vienna
Metabolomics Center (University of Vienna) for metaproteomic analysis.
Peptides were re-suspended in 1 \si{\percent} (final concentration) TFA,
desalted using the Pierce C18 Tips (Thermo Fisher Scientific, USA)
according to the manufacturer's instructions and sequenced on a Q
Exactive Hybrid Quadrupole-Orbitrap Mass Spectrometer (Thermo Fisher
Scientific, USA). Obtained MS/MS spectra were searched against a protein
database composed of combined sequenced metagenomes using SEQUEST-HT
engines and validated with Percolator in Proteome Discoverer 2.1 (Thermo
Fisher Scientific, USA). The target-decoy approach was used to reduce
the probability of false peptide identification. Results whose false
discovery rate at the peptide level was \textless{} \SI{1}{\percent}
were kept. For protein identification a minimum of two peptides and one
unique peptide were required. For protein quantification, a
chromatographic peak area-based free quantitative method was applied.

@@

Processing and visualization of 16S rRNA, metagenomic and metaproteomic
data were done using R (version 3.6.0) (R Core Team, 2019), package
tidyverse (version 1.3.0) (Wickham et al., 2019) and multiple other
packages (Neuwirth, 2014; Xie, 2014, 2015, 2019, 2020; Wilke, 2018; Xie
et al., 2018; Allaire et al., 2019; Zhu, 2019; Bengtsson, 2020). The
detailed analysis procedure including the R Markdown file for this paper
are available as a GitHub repository
(\url{https://github.com/MicrobesRovinj/Korlevic_SelectiveRemoval_FrontMicrobiol_2021}).

@@

To evaluate whether the obtained DNA is suitable to determine the
composition of the microbial community Illumina sequencing of the V4
region of the 16S rRNA was performed. Sequencing yielded a total of
336,944 sequences after quality curation and exclusion of eukaryotic,
mitochondrial and no relative sequences. The number of sequences
classified as chloroplasts was 97,334. After excluding these sequences,
the total number of retrieved reads was 239,610, ranging from 22,596 to
52,930 sequences per sample (\autoref{supp-nseq_notus}). Even when the
highest sequencing effort was applied, the rarefaction curves did not
level off which is commonly observed in high-throughput 16S rRNA
amplicon sequencing (\autoref{supp-rarefaction}). Sequences clustering
at a similarity level of 97 \si{\percent} yielded a total of 8,355
different OTUs. Taxonomic classification of reads revealed a
macrophyte-associated epiphytic community that mainly composed of
\emph{Alphaproteobacteria} (14.9 ± 3.5 \si{\percent}),
\emph{Bacteroidota} (12.5 ± 2.4 \si{\percent}),
\emph{Gammaproteobacteria} (11.6 ± 4.3 \si{\percent}),
\emph{Desulfobacterota} (7.8 ± 7.5 \si{\percent}), \emph{Cyanobacteria}
(6.5 ± 4.7 \si{\percent}) and \emph{Planctomycetota} (2.9 ± 1.7
\si{\percent}) (\autoref{community}).

@@

Successful amplification and sequencing of the V4 region of the 16S rRNA
gene proved that the isolated DNA can be used to estimate the microbial
epiphytic diversity. Taxonomic groups detected in this step can also be
often found in epiphytic communities associated with other macrophytes
(Burke et al., 2011b; Morrissey et al., 2019). A problem often
encountered in studies focusing on epiphytic communities is the presence
of large proportions of chloroplast 16S rRNA sequences in the pool of
amplified molecules, especially if the epiphytic DNA was isolated
without prior selection (Staufenberger et al., 2008). These sequences
can derive from host chloroplasts or from eukaryotic epiphytic
chloroplast DNA. Although the proportion of obtained chloroplast 16S
rRNA sequences in our samples was substantial, they derived almost
exclusively from eukaryotic epiphytes. High proportion of chloroplast
16S rRNA sequences in studies applying selective procedures that include
direct cellular lysis on host surfaces were observed before (Michelou et
al., 2013). It is possible that chloroplast-specific sequences even in
these studies originated from eukaryotic epiphytic cells and not from
host chloroplasts. Indeed, it is common during 16S rRNA profiling of
pelagic microbial communities to observe high proportions of chloroplast
sequences (Gilbert et al., 2009; Korlević et al., 2016). In addition, a
very low proportion of chloroplast 16S rRNA sequences in samples
originating from \emph{C. cylindracea} in comparison to \emph{C. nodosa}
could be explained by the presence of three introns in the gene for 16S
rRNA in some members of the genus \emph{Caulerpa} that could hamper the
amplification process (Lam and Lopez-Bautista, 2016).

@@

\leavevmode\hypertarget{ref-Cole2014}{}%
Cole, J. R., Wang, Q., Fish, J. A., Chai, B., McGarrell, D. M., Sun, Y.,
et al. (2014). Ribosomal Database Project: Data and tools for high
throughput rRNA analysis. \emph{Nucleic Acids Res} 42, D633--D642.
doi:\href{https://doi.org/10.1093/nar/gkt1244}{10.1093/nar/gkt1244}.

@@

@@

\leavevmode\hypertarget{ref-Huerta-Cepas2019}{}%
Huerta-Cepas, J., Szklarczyk, D., Heller, D., Hernández-Plaza, A.,
Forslund, S. K., Cook, H., et al. (2019). eggNOG 5.0: A hierarchical,
functionally and phylogenetically annotated orthology resource based on
5090 organisms and 2502 viruses. \emph{Nucleic Acids Res} 47,
D309--D314.
doi:\href{https://doi.org/10.1093/nar/gky1085}{10.1093/nar/gky1085}.

@@

\leavevmode\hypertarget{ref-Hyatt2010}{}%
Hyatt, D., Chen, G.-L., LoCascio, P. F., Land, M. L., Larimer, F. W.,
and Hauser, L. J. (2010). Prodigal: Prokaryotic gene recognition and
translation initiation site identification. \emph{BMC Bioinformatics}
11, 119.
doi:\href{https://doi.org/10.1186/1471-2105-11-119}{10.1186/1471-2105-11-119}.

\leavevmode\hypertarget{ref-Jiang2015}{}%
Jiang, Y.-F., Ling, J., Dong, J.-D., Chen, B., Zhang, Y.-Y., Zhang,
Y.-Z., et al. (2015). Illumina-based analysis the microbial diversity
associated with \emph{Thalassia hemprichii} in Xincun Bay, South China
Sea. \emph{Ecotoxicology} 24, 1548--56.
doi:\href{https://doi.org/10.1007/s10646-015-1511-z}{10.1007/s10646-015-1511-z}.

@@

\leavevmode\hypertarget{ref-Leary2014}{}%
Leary, D. H., Li, R. W., Hamdan, L. J., IV, W. J. H., Lebedev, N., Wang,
Z., et al. (2014). Integrated metagenomic and metaproteomic analyses of
marine biofilm communities. \emph{Biofouling} 30, 1211--1223.
doi:\href{https://doi.org/10.1080/08927014.2014.977267}{10.1080/08927014.2014.977267}.

@@

\leavevmode\hypertarget{ref-Michelou2013}{}%
Michelou, V. K., Caporaso, J. G., Knight, R., and Palumbi, S. R. (2013).
The ecology of microbial communities associated with \emph{Macrocystis
pyrifera}. \emph{PloS One} 8, e67480.
doi:\href{https://doi.org/10.1371/journal.pone.0067480}{10.1371/journal.pone.0067480}.

@@

\leavevmode\hypertarget{ref-Xie2014}{}%
Xie, Y. (2014). `` knitr: A comprehensive tool for reproducible research
in R,'' in \emph{Implementing Reproducible Computational Research}, eds.
V. Stodden, F. Leisch, and R. D. Peng (New York: Chapman and Hall/CRC),
3--32.

@@

\leavevmode\hypertarget{ref-Xie2019a}{}%
Xie, Y. (2019). TinyTeX: A lightweight, cross-platform, and
easy-to-maintain LaTeX distribution based on TeX Live. \emph{TUGboat}
40, 30--32.

\leavevmode\hypertarget{ref-Xie2020}{}%
Xie, Y. (2020). \emph{tinytex: Helper functions to install and maintain
'TeX Live', and compile 'LaTeX' documents}.

>>>>

\hypertarget{abstract}{%
\subsection{Abstract}\label{abstract}}

@@

Leaves of \emph{C. nodosa} were sampled in a \emph{C. nodosa} meadow in
the Bay of Saline, northern Adriatic Sea (\ang{45;7;5} N, \ang{13;37;20}
E) and in a \emph{C. nodosa} meadow invaded by \emph{C. cylindracea} in
the Bay of Funtana, northern Adriatic Sea (\ang{45;10;39} N,
\ang{13;35;42} E). Thalli of \emph{C. cylindracea} were sampled in the
same \emph{C. nodosa} invaded meadow in the Bay of Funtana and at a
locality of only \emph{C. cylindracea} located in the proximity of the
invaded meadow. Leaves and thalli for 16S rRNA analysis, metagenomics
and metaproteomics were collected in two contrasting seasons, on 4
December 2017 (16S rRNA analysis and metaproteomics), 14 December 2017
(metagenomics) and 18 June 2018 (16S rRNA analysis, metagenomics and
metaproteomics). During spring 2018, the \emph{C. nodosa} meadow in the
Bay of Saline decayed to an extent that no leaves could be retrieved
(Najdek et al., 2020). In addition, as not enough DNA for both
metagenomic and 16S RNA analysis were obtained during the sampling on 4
December 2017, an additional sampling on 14 December 2017 was carried
out in the Bay of Funtana. Leaves and thalli were collected by diving
and transported to the laboratory in containers placed on ice and filled
with seawater from the site. Upon arrival to the laboratory, \emph{C.
nodosa} leaves were cut into sections of 1 -- 2 \si{\cm}, while \emph{C.
cylindracea} thalli were cut into 5 -- 8 \si{\cm} long sections. Leaves
and thalli were washed three times with sterile artificial seawater
(ASW) to remove loosely attached microbial cells.

@@

An aliquot of isolated DNA was treated with RNase A (final concentration
200 \si{\ug\per\ml}) for 2 \si{\hour} at 37 \si{\degreeCelsius}. The DNA
concentration was determined using the Quant-iT PicoGreen dsDNA Assay
Kit (Invitrogen, USA) according to the manufacturer's instructions and
diluted to 1 \si{\ng\per\ul}. The V4 region of the 16S rRNA gene was
amplified using a two-step PCR procedure. In the first PCR the 515F
(\(5'\)-GTGYCAGCMGCCGCGGTAA-\(3'\)) and 806R
(\(5'\)-GGACTACNVGGGTWTCTAAT-\(3'\)) primers from the Earth Microbiome
Project (\url{https://earthmicrobiome.org/protocols-and-standards/16s/})
were used to amplify the target region (Caporaso et al., 2012; Apprill
et al., 2015; Parada et al., 2016). These primers contained on their
\(5'\) end a tagged sequence. Each sample was amplified in four parallel
25 \si{\ul} reactions of which each contained 1 × Q5 Reaction Buffer,
0.2 \si{\milli\Molar} dNTPmix, 0.7 \si{\mg\per\ml} BSA (Bovine Serum
Albumin), 0.2 \si{\micro\Molar} of forward and reverse primers, 0.5 U of
Q5 High-Fidelity DNA Polymerase (New England Biolabs, USA) and 5
\si{\ng} of DNA template. Cycling conditions were: initial denaturation
at 94 \si{\degreeCelsius} for 3 \si{\minute}, 20 cycles of denaturation
at 94 \si{\degreeCelsius} for 45 \si{\s}, annealing at 50
\si{\degreeCelsius} for 60 \si{\s} and elongation at 72
\si{\degreeCelsius} for 90 \si{\s}, finalized by an elongation step at
72 \si{\degreeCelsius} for 10 \si{\minute}. The four parallel reactions
volumes were pooled and PCR products were purified using the GeneJET PCR
Purification Kit (Thermo Fisher Scientific, USA) according to the
manufacturer's instructions and following the protocol that included
isopropanol addition for better small DNA fragment yield. The column was
eluted in 30 \si{\ul} of deionized water. Purified PCR products were
sent for Illumina MiSeq sequencing (2 × 250 bp) at IMGM Laboratories,
Martinsried, Germany. Before sequencing at IMGM, the second PCR
amplification of the two-step PCR procedure was performed using primers
targeting the tagged region incorporated in the first PCR. In addition,
these primers contained adapter and sample-specific index sequences. The
second PCR was carried out for 8 cycles. Beside samples, a positive and
negative control were sequenced. A negative control was comprised of
four parallel PCR reactions without DNA template, while for a positive
control a mock community composed of evenly mixed DNA material
originating from 20 bacterial strains (ATCC MSA-1002, ATCC, USA) was
used. Partial 16S rRNA sequences obtained in this study have been
deposited in the European Nucleotide Archive (ENA) at EMBL-EBI under
accession numbers SAMEA6786270, SAMEA6648792 -- SAMEA6648794,
SAMEA6648809 -- SAMEA6648811 and SAMEA6648824.

@@

Isolated proteins were whole trypsin digested using the FASP
(filter-aided sample preparation) Protein Digestion Kit (Expedeon, UK)
according to the manufacturer's instructions with small modifications
(Wiśniewski et al., 2009). Prior to loading the solution onto the
column, protein pellets were solubilized in urea sample buffer included
in the kit amended with DTT (final concentration 100 \si{\milli\Molar})
for 45 \si{\minute} at room temperature and centrifuged at 20,000 × g
for 2 -- 5 \si{\minute} at room temperature to remove larger particles.
The first washing step after protein solution loading was repeated
twice. In addition, the centrifugation steps were prolonged if the
column was clogged. Trypsin digestion was performed on column filters at
37 \si{\degreeCelsius} overnight for 18 \si{\hour}. The final filtrate
containing peptides was acidified with 1 \si{\percent} (final
concentration) trifluoroacetic acid (TFA), freezed at \num{-80}
\si{\degreeCelsius}, lyophilized and sent to VIME -- Vienna Metabolomics
Center (University of Vienna) for metaproteomic analysis. Peptides were
re-suspended in 1 \si{\percent} (final concentration) TFA, desalted
using the Pierce C18 Tips (Thermo Fisher Scientific, USA) according to
the manufacturer's instructions and sequenced on a Q Exactive Hybrid
Quadrupole-Orbitrap Mass Spectrometer (Thermo Fisher Scientific, USA).
Obtained MS/MS spectra were searched against a protein database composed
of combined sequenced metagenomes obtained in this study using
SEQUEST-HT engines and validated with Percolator in Proteome Discoverer
2.1 (Thermo Fisher Scientific, USA). The target-decoy approach was used
to reduce the probability of false peptide identification. Results whose
false discovery rate at the peptide level was \textless{}
\SI{1}{\percent} were kept. For protein identification a minimum of two
peptides and one unique peptide were required. For protein
quantification, a chromatographic peak area-based free quantitative
method was applied.

@@

Processing and visualization of 16S rRNA, metagenomic and metaproteomic
data were done using R (version 3.6.0) (R Core Team, 2019), package
tidyverse (version 1.3.0) (Wickham et al., 2019) and multiple other
packages (Neuwirth, 2014; Xie, 2014, 2015, 2019a, 2019b; Wilke, 2018;
Xie et al., 2018; Allaire et al., 2019; Zhu, 2019; Bengtsson, 2020). The
detailed analysis procedure including the R Markdown file for this paper
are available as a GitHub repository
(\url{https://github.com/MicrobesRovinj/Korlevic_SelectiveRemoval_FrontMicrobiol_2021}).

@@

To evaluate whether the obtained DNA is suitable to determine the
composition of the microbial community Illumina sequencing of the V4
region of the 16S rRNA was performed. Sequencing yielded a total of
292,888 sequences after quality curation and exclusion of eukaryotic,
mitochondrial and no relative sequences. The number of sequences
classified as chloroplasts was 97,331. After excluding these sequences,
the total number of retrieved reads was 195,557, ranging from 13,667 to
41,842 sequences per sample (\autoref{supp-nseq_notus}). Even when the
highest sequencing effort was applied, the rarefaction curves did not
level off which is commonly observed in high-throughput 16S rRNA
amplicon sequencing (\autoref{supp-rarefaction}). Sequences clustering
at a similarity level of 97 \si{\percent} yielded a total of 8,355
different OTUs. Taxonomic classification of reads revealed a
macrophyte-associated epiphytic community mainly composed of
\emph{Alphaproteobacteria} (14.9 ± 3.5 \si{\percent}),
\emph{Bacteroidota} (12.5 ± 2.4 \si{\percent}),
\emph{Gammaproteobacteria} (11.6 ± 4.3 \si{\percent}),
\emph{Desulfobacterota} (7.8 ± 7.5 \si{\percent}), \emph{Cyanobacteria}
(6.5 ± 4.7 \si{\percent}) and \emph{Planctomycetota} (2.9 ± 1.7
\si{\percent}) (\autoref{community}).

@@

Successful amplification and sequencing of the V4 region of the 16S rRNA
gene proved that the isolated DNA can be used to estimate the microbial
epiphytic diversity. Taxonomic groups detected in this step can also be
often found in epiphytic communities associated with other macrophytes
(Burke et al., 2011b; Morrissey et al., 2019). A problem often
encountered in studies focusing on epiphytic communities is the presence
of large proportions of chloroplast 16S rRNA sequences in the pool of
amplified molecules, especially if the epiphytic DNA was isolated
without prior selection (Staufenberger et al., 2008). These sequences
can derive from host chloroplasts or from eukaryotic epiphytic
chloroplast DNA. Although the proportion of obtained chloroplast 16S
rRNA sequences in our samples was substantial, they derived almost
exclusively from eukaryotic epiphytes. High proportion of chloroplast
16S rRNA sequences in studies applying selective procedures that include
direct cellular lysis on host surfaces were observed before (Michelou et
al., 2013). It is possible that chloroplast-specific sequences even in
these studies originated from eukaryotic epiphytic cells and not from
host chloroplasts. Indeed, it is common during 16S rRNA profiling of
pelagic microbial communities to observe high proportions of chloroplast
sequences (Gilbert et al., 2009; Korlević et al., 2016). On of the
solutions to further reduce chloroplast 16S rRNA sequence contamination
is to use primers that minimise the amplification of these reads if the
sequencing and study design allow it (Hanshew et al., 2013). In
addition, a very low proportion of chloroplast 16S rRNA sequences in
samples originating from \emph{C. cylindracea} in comparison to \emph{C.
nodosa} could be explained by the presence of three introns in the gene
for 16S rRNA in some members of the genus \emph{Caulerpa} that could
hamper the amplification process (Lam and Lopez-Bautista, 2016).

@@

\leavevmode\hypertarget{ref-Cole2014}{}%
Cole, J. R., Wang, Q., Fish, J. A., Chai, B., McGarrell, D. M., Sun, Y.,
et al. (2014). Ribosomal Database Project: Data and tools for high
throughput rRNA analysis. \emph{Nucleic Acids Res.} 42, D633--D642.
doi:\href{https://doi.org/10.1093/nar/gkt1244}{10.1093/nar/gkt1244}.

@@

\leavevmode\hypertarget{ref-Hanshew2013}{}%
Hanshew, A. S., Mason, C. J., Raffa, K. F., and Currie, C. R. (2013).
Minimization of chloroplast contamination in 16S rRNA gene
pyrosequencing of insect herbivore bacterial communities. \emph{J.
Microbiol. Methods} 95, 149--155.
doi:\href{https://doi.org/10.1016/j.mimet.2013.08.007}{10.1016/j.mimet.2013.08.007}.

@@

\leavevmode\hypertarget{ref-Huerta-Cepas2019}{}%
Huerta-Cepas, J., Szklarczyk, D., Heller, D., Hernández-Plaza, A.,
Forslund, S. K., Cook, H., et al. (2019). eggNOG 5.0: A hierarchical,
functionally and phylogenetically annotated orthology resource based on
5090 organisms and 2502 viruses. \emph{Nucleic Acids Res.} 47,
D309--D314.
doi:\href{https://doi.org/10.1093/nar/gky1085}{10.1093/nar/gky1085}.

@@

\leavevmode\hypertarget{ref-Hyatt2010}{}%
Hyatt, D., Chen, G.-L., LoCascio, P. F., Land, M. L., Larimer, F. W.,
and Hauser, L. J. (2010). Prodigal: Prokaryotic gene recognition and
translation initiation site identification. \emph{BMC Bioinf.} 11, 119.
doi:\href{https://doi.org/10.1186/1471-2105-11-119}{10.1186/1471-2105-11-119}.

\leavevmode\hypertarget{ref-Jiang2015}{}%
Jiang, Y.-F., Ling, J., Dong, J.-D., Chen, B., Zhang, Y.-Y., Zhang,
Y.-Z., et al. (2015). Illumina-based analysis the microbial diversity
associated with \emph{Thalassia hemprichii} in Xincun Bay, South China
Sea. \emph{Ecotoxicology} 24, 1548--1556.
doi:\href{https://doi.org/10.1007/s10646-015-1511-z}{10.1007/s10646-015-1511-z}.

@@

\leavevmode\hypertarget{ref-Leary2014}{}%
Leary, D. H., Li, R. W., Hamdan, L. J., Judson Hervey IV, W., Lebedev,
N., Wang, Z., et al. (2014). Integrated metagenomic and metaproteomic
analyses of marine biofilm communities. \emph{Biofouling} 30,
1211--1223.
doi:\href{https://doi.org/10.1080/08927014.2014.977267}{10.1080/08927014.2014.977267}.

@@

\leavevmode\hypertarget{ref-Michelou2013}{}%
Michelou, V. K., Caporaso, J. G., Knight, R., and Palumbi, S. R. (2013).
The ecology of microbial communities associated with \emph{Macrocystis
pyrifera}. \emph{PLoS One} 8, e67480.
doi:\href{https://doi.org/10.1371/journal.pone.0067480}{10.1371/journal.pone.0067480}.

@@

\leavevmode\hypertarget{ref-Xie2014}{}%
Xie, Y. (2014). ``knitr: A comprehensive tool for reproducible research
in R,'' in \emph{Implementing Reproducible Computational Research}, eds.
V. Stodden, F. Leisch, and R. D. Peng (New York: Chapman and Hall/CRC),
3--32.

@@

\leavevmode\hypertarget{ref-Xie2019a}{}%
Xie, Y. (2019a). TinyTeX: A lightweight, cross-platform, and
easy-to-maintain LaTeX distribution based on TeX Live. \emph{TUGboat}
40, 30--32.

\leavevmode\hypertarget{ref-Xie2019b}{}%
Xie, Y. (2019b). \emph{tinytex: Helper functions to install and maintain
'TeX Live', and compile 'LaTeX' documents}.
